Fusion Moves for Correlation Clustering

### 2014-11-11 paper/introduction-new.tex
introduction in progress

\vspace{0.1cm}
\noindent \textbf{Related Work.}
A natural approach is to solve the integer linear programming problem directly. To this end, efficient separation procedures have been found \cite{} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation. Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning. The latter approach works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.

Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{kroeger_2014_cvpr}. The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs. Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}.

>>>>

\vspace{0.1cm}
\noindent \textbf{Related Work.}
A natural approach is to solve the integer linear programming problem directly. 
To this end, efficient separation procedures have been found~\cite{kappes_2011_emmcvpr,kappes_2013_arxiv} that allow to iteratively augment the set of constraints until a valid partitioning is found. 
Alternatively, it is possible to relax the integrality constraints of the integer linear programming formulation~\cite{kappes_2013_arxiv}. 
Such an outer relaxation can be iteratively tightened. However, intermediate solutions are fractional and so rounding is required to obtain a valid partitioning.
For the latter approach column generating methods exits, that works best on planar \cite{yarkony_2012_eccv} or almost planar \cite{yarkony-andres-2013} graphs.

Another line of work maintains valid partitionings throughout, either by using a cluster representation in terms of labels \cite{bagon_2011_arxiv} or in terms of cut edges \cite{beier_2014_cvpr}. 
The former suffers \cite{beier} from the degeneracy of a label presentation \cite{kappes}, while the latter is highly efficient only for planar graphs.
% Working on contracted nodes has previously been explored in \cite{kroeger_2013_miccai}. 
An other branch of research uses move making algorithm 
to optimize correlation clustering~\cite{bansal_2004_ml,beier_2014_cvpr,Kernighan-1970}.
Starting with an initial segmentation, auxiliary problems are solved that 
strictly improve the segmentation.
